---
title: "Reproducing Results of Gerard and Stephens (2017)"
bibliography: readme_bib.bib
output: github_document
---

# Introduction

This repository contains code to reproduce the empirical evaluations
of @gerard2017unifying. The new methods can be found in the
[vicar](https://github.com/dcgerard/vicar) package.

```{r, echo = FALSE, results = "hide", message=FALSE}
liblist <- list("tidyverse", "stringr", "pROC",
                "ruv", "cate", "gridExtra", "snow", "devtools", "sva",
                "limma", "vicar", "seqgendiff", "assertthat", "R.utils", 
                "broom")
lapply(liblist, library, character.only = TRUE)
```

If you are having trouble reproducing these results, it might be that you need to update some of your R packages. These are the versions that I used:

```{r}
sessionInfo()
```

I've also only tried this out on Ubuntu.

If you find a bug, please create an
[issue](https://github.com/dcgerard/ruvb_sims/issues).

# Instructions

To reproduce the results of @gerard2017unifying, you need to (1)
install the appropriate R packages, (2) obtain the appropriate data,
(3) run `make` and (4) get some coffee while you wait.

## Install R Packages

To install the needed R packages, run the following in R

```{r, eval=FALSE}
devtools::install_version("ruv", 
                          version = "0.9.6", 
                          repos = "http://cran.us.r-project.org")
install.packages(c("tidyverse", "pROC", "cate", "gridExtra", "broom",
                   "snow", "devtools", "assertthat", "R.utils",
                   "BiocManager"))
BiocManager::install(c("sva", "limma"), update = FALSE)
devtools::install_github("dcgerard/vicar",
                         ref = "e7caad35b403d83546680a89f5af2b3b4ed5fe6a")
devtools::install_github("dcgerard/seqgendiff",
                         ref = "a2fe006e8012cbfe5295e6212938e9fb865be63b")
```

- `ruv` was updated and now the equivalencies between the `vicar` method and
   the `ruv` method are not *exactly* the same. This is why we install 
   version 0.9.6 of `ruv`.
   
- Newer versions of `seqgendiff` should not work as the `poisthin()` function has been replaced by `select_counts()` and `thin_2group()`.

## Get Data

Place the following files in the Data folder:

1. [GTEx_Data_V6_Annotations_SampleAttributesDS.txt](http://www.gtexportal.org/home/datasets#filesetFilesDiv21)
2. [GTEx_Analysis_v6p_RNA-seq_RNA-SeQCv1.1.8_gene_reads.gct.gz](http://www.gtexportal.org/home/datasets#filesetFilesDiv11)

These files are only available if you are a registered
user of the GTEx Portal. You can create a free account at 
<https://gtexportal.org/>

## Run Make

To reproduce all of the results in @gerard2017unifying, simply run
`make` from the terminal.

If you want to reproduce just the simulation results in the main text, run
``` bash
make sims
```

If you want to reproduce the supplementary simulations with correlated
confounders, run
``` bash
make corr
```

If you want to reproduce the supplementary simulations with misspecified
negative controls, run
``` bash
make miss
```

If you want to reproduce the figure in the introduction, run
``` bash
make one_data
```

## Get Coffee

These runs should take a very long time
(a day to a couple of days). You should get some coffee. Here is a list of some of my favorite places:

* Washington, DC
    - [Colony Club](https://www.yelp.com/biz/colony-club-washington)
    - [Grace Street Coffee](https://www.yelp.com/biz/grace-street-coffee-georgetown)
    - [Shop Made in DC](https://www.yelp.com/biz/shop-made-in-dc-washington)
* Chicago
    - [Sawada Coffee](https://www.yelp.com/biz/sawada-coffee-chicago)
    - [Plein Air Cafe](https://www.yelp.com/biz/plein-air-cafe-and-eatery-chicago-2)
* Seattle
    - [Bauhaus Ballard](https://www.yelp.com/biz/bauhaus-ballard-seattle)
    - [Cafe Solstice](https://www.yelp.com/biz/cafe-solstice-seattle)
* Columbus
    - [Yeah, Me Too](https://www.yelp.com/biz/yeah-me-too-columbus)
    - [Stauf's Coffee Roasters](https://www.yelp.com/biz/staufs-coffee-roasters-columbus-2)

# References
